---
title: "ChemdooleBasics.Rmd"
author: "zachcp"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

## ChemDoodle WebComponents 

This repo is for the creation of an HTMLWidget for visualizing
moleules based on the [ChemDoodle WebComponent](http://web.chemdoodle.chttps://github.com/rajarshi/cdkr/tree/master/rcdkom/) library,
the [HTMLWidgets](http://www.htmlwidgets.org/) package, and the
[Chemistry Development Kit](https://github.com/cdk) via [rCDK](https://github.com/rajarshi/cdkr/tree/master/rcdk). **Warning: development in flux and liable to break until version 1.0!**

### Basic Viewer

```{r}
library(chemdoodle)
chemdoodle_viewer("C1CCCCC1", width = 100, height = 100)
```

### Transform Canvas

```{r}
chemdoodle_transform("C1CCCCC1", width = 100, height = 100)
```


### Slideshow Canvas

```{r}
chemdoodle_slideshow(c("C1CCCCC1", "CNCNCNC1CCCCC1", "CN1C=NC2=C1C(=O)N(C(=O)N2C)C",
                       "CC1=C(C=C(C2=C1C(=C)OC2=O)OC)OC"), 200,200, bondscale=15)

```

### Sketcher

The ChemDoodle Sketcher needs extra work for functionality. You can use `drawMolecule()` to create a seketcher and the molecule is captured as ChemDoodle JSON which can be converted to
a CDK Atom and be passed around, converter or whatever. Currently round-tripping (putting the molecule back) doesn't work because there are some issues around properly scaling the compound.


```{r, eval=FALSE}
#experimetal/new features

# gets a molecule from the chemdoodle sketcher
moljson <- drawMolecule()

# processed the Molecule JSON to a CDK AtomContainer - this can be saved,
# written to Smiles etc.
mol <- processChemDoodleJson(moljson)

# convert to SMILES
smi <- toSmiles(mol)

# convert to InChi
inchi <- toInChi(mol)

# try sending a molecule to the sketcher (needs work)
drawMolecule(mol=mol)

```

### Access the Sketcher as a ShinyApp 

```{r, eval=FALSE}
# you can also try a minimal shiny example
shiny::runApp(appDir = "examples/minimalshinyapp/")
```
